FoRTE baseline

### 2019-09-12 analysis/paper/paper.Rmd
More work on Discussion

Our first question was: To what extent can the model, under any configuration, reproduce the observed reality?
**Ensemble mean trajectory matches traditional understanding of succession**---rapid growth to peak productivity, followed by gradual decline [@odum_1969_strategy_ecosystem_development]---but **happens too quickly** (Figure 2);
real ecosystems sustain peak productivity for longer [@gough_2016_disturbance].
This idea that ED2.2's main issue is that it is moving too quickly is supported by the fact that ED2.2 generally **underestimates productivity after 100 years**, but model **predictions at peak productivity are close to reality**.
One reason ED2.2 is moving too quickly through succession is **missing mechanisms for sustaining productivity through early succession**.
In particular, recent evidence points to the **important role of low-severity, high-frequency disturbances** in sustaining ecosystem productivity [@gough_2016_disturbance].
ED2.2 has a mortality scheme, and indeed, parameters related to mortality were often among the top 10 most important parameters for predictive uncertainty (Figure 6).
<!-- Maybe move this elsewhere? -->
<!-- TODO Look at mortality across ED runs. Does it relate at all to results? -->
However, **our simulations did not include other sources of disturbance**, such as partial harvests, extreme weather, and damage from insects and pathogens, which are common to this region [@amiro_2010_ecosystem] and which may contribute to sustaining productivity and dominance of early-successional forests [@gough_2016_disturbance].
Future work will: (1) Calibrate ED2.2 disturbance response to experimental observations (FoRTE), and (2) run long-term simulations with prescribed disturbance frequencies and see how they affect ecological dynamics.

@@

**Parameter uncertainty was the dominant driver of uncertainty in our analysis**.
Different parameter combinations led to **huge ranges in ensemble predictions of ensemble variables** -- NPP ranged from 0 to almost 2x the observed, and LAI was up to 3x observed (though more tightly clustered around zero) (Figure 2).
Moreover, different parameter combinations produced **qualitatively different ecological narratives** (Figure 4).
**Parameter uncertainty has implications beyond C cycling**---differences in species composition and relative abundance have implications for forest management and wildlife conservation, among others.

**Parameter uncertainty is not synonymous with sensitivity**.
Many of the parameters to which model outputs are most sensitive are already well constrained by data and do not contribute as much to predictive uncertainty (Figure 6).
Although parameter uncertainty is still large, this means that **targeted data collection works and that we are moving in the right direction**!
This speaks to the value of looking at not just sensitivity, but partial variance [@lebauer_2013_facilitating; @dietze_2014_quantitative].
(Compare sensitivity results to these studies, and also to @pandit_2018_optimizing).

>>>>

Our first question was: To what extent can the model, under any configuration, reproduce the observed reality?
**Ensemble mean trajectory matches traditional understanding of succession**---rapid growth to peak productivity, followed by gradual decline [@odum_1969_strategy_ecosystem_development]---but **happens too quickly** (Figure 2);
real ecosystems sustain peak productivity for longer [@gough_2016_disturbance].
This idea that ED2.2's main issue is that it is moving too quickly is supported by the fact that ED2.2 generally underestimates productivity after 100 years, but model **predictions at peak productivity are close to reality**.
One reason ED2.2 is moving too quickly through succession is **missing mechanisms for sustaining productivity through early succession**.
In particular, recent evidence points to the **important role of low-severity, high-frequency disturbances** in sustaining ecosystem productivity [@gough_2016_disturbance].
ED2.2 has a mortality scheme, and indeed, parameters related to mortality were often among the top 10 most important parameters for predictive uncertainty (Figure 6).
<!-- Maybe move this elsewhere? -->
<!-- TODO Look at mortality across ED runs. Does it relate at all to results? -->
However, **our simulations did not include other sources of disturbance**, such as partial harvests, extreme weather, and damage from insects and pathogens, which are common to this region [@amiro_2010_ecosystem] and which may contribute to sustaining productivity and dominance of early-successional forests [@gough_2016_disturbance].
Future work will: (1) Calibrate ED2.2 disturbance response to experimental observations (FoRTE), and (2) run long-term simulations with prescribed disturbance frequencies and see how they affect ecological dynamics.

@@

**Parameter uncertainty was the dominant driver of uncertainty in our analysis**.
Different parameter combinations led to **huge ranges in ensemble predictions of ensemble variables** -- NPP ranged from 0 to almost 2x the observed, and LAI was up to 3x observed (though more tightly clustered around zero) (Figure 2).
Moreover, different parameter combinations produced **qualitatively different ecological narratives** (Figure 4).
**Parameter uncertainty has implications beyond C cycling**---differences in species composition and relative abundance have implications for forest management and wildlife conservation, among others.
The dominance of parameter uncertainty over structural uncertainty in our results suggests that **targeted data collection should be a higher priority than model development**.

**Parameter uncertainty is not synonymous with sensitivity**.
Many of the parameters to which model outputs are most sensitive are already well constrained by data and do not contribute as much to predictive uncertainty (Figure 6).
Although parameter uncertainty is still large, this means that **targeted data collection works and that we are moving in the right direction**!
This speaks to the value of looking at not just sensitivity, but partial variance [@lebauer_2013_facilitating; @dietze_2014_quantitative].

So **which parameters are a research priority**?
Leaf optical properties often do not get a lot of attention, but are important [see also, @viskari_2019_influence].
Also, soil-plant water conductance and growth respiration -- both of these were important in @dietze_2014_quantitative.
(Compare also to @raczka_2018_what, @pandit_2018_optimizing).
